Untitled

### 2023-08-21 code/analysis_Redo.Rmd
cleaned up grouped analysis

## NumberofPatients and Total.Hours are the best cases, controlling for Sites
```{r}
df.spill3 <- df.spill2 %>% 
  left_join(census %>% select(ZipCode, YEAR, IncomeBelowPoverty, PovertyStatusDet), by = c("Year" = "YEAR", "Zip" = "ZipCode"))#%>% 
  # mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet, 
  #        Unemployed = Unemployed / Unemp_denom, 
  #        Elderly = Age65andOver / TotalPop, 
  #        Black = Black / TotalPop, 
  #        Hispanic = Hispanic / TotalPop)

@@

 did.access.figures %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","Estimate","95% CI")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Patients" = 5, "Intensive Margin" = 2, "Extensive Margin" = 2)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "TE" = 2,"TE * Distance" = 2))

>>>>

## NumberofPatients and Total.Hours are the best cases, controlling for Sites
```{r}

zipsize2 <- zctas(starts_with = unique(c(df.spill2$Zip)), year = 2010)

df.spill3 <- df.spill2 %>% 
  left_join(census %>% select(ZipCode, YEAR, TotalPop, IncomeBelowPoverty, PovertyStatusDet), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
  left_join(zipsize2 %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6, 
         l.popdensity = log(TotalPop / Area.SQmiles))
  # mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet, 
  #        Unemployed = Unemployed / Unemp_denom, 
  #        Elderly = Age65andOver / TotalPop, 
  #        Black = Black / TotalPop, 
  #        Hispanic = Hispanic / TotalPop)

@@

 did.access.figures %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","Estimate","95% CI")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Patients" = 5, "Access" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "TE" = 2,"TE * Distance" = 2))
